Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
starting to address comments

The formal statistical errors on these parameters are small. Just as in the 
case of performing the regression versus  H\,\textsc{i}, systematic problems 
will dominate the uncertainty in the derived zero point offset. The systematics
likely to dominate our FDS-based zero level are imperfect zodiacal light 
corrections and the FDS99 temperature map. To quantify the level of systematic 
error, we split the sky into four quadrants, with the dividing boundaries being
 $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted to
 $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
quadrant. The slopes varied from 0.948 to 0.993, with an rms of 0.0188, while 
the offsets varied from $-$0.056 MJy/sr to $+$0.089 MJy/sr, with an rms of 
0.0586 MJy/sr.

>>>>

The formal statistical errors on these parameters are small. Just as in the 
case of performing the regression versus  H\,\textsc{i}, systematic problems 
dominate the uncertainty in the derived zero point offset. The systematics
likely to dominate our FDS-based zero level are imperfect zodiacal light 
corrections and the FDS99 temperature map. To quantify the level of systematic 
error, we split the sky into four quadrants, with the dividing boundaries being
$b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted to
$\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
quadrant. The slopes varied from 0.948 to 0.993, with an rms of 0.0188, while 
the offsets varied from $-$0.056 MJy/sr to $+$0.089 MJy/sr, with an rms of 
0.0586 MJy/sr.
